### 2019-06-21 README.Rmd
added talking point to readme and lime image
updated to do list

# LIME Research

@@

- can I remove some of the sources from the references file that I am not going to use?
- I finished writing and editing the introduction - what do you think?

@@

- draft background section
- fix outline of the rest of the paper now that I have a clear vision
- read through papers giving an overview of the current explanation methods

@@

- finish journal on understanding lime (look at the RF in the local region
  lime is considering to see if it agrees with the lime explanations)
- think about how the argmin is accomplished by the LIME R package
- change distance matrix in seriation to be 5-# of variables shared between two rows
  or try using distance matrix computed on the feature values
- fix issue with seriation
- try fitting LASSO logistic model and leave one out approach (for multicollinarity)
- assess lime results on logistic regression models
- think about how to implement a simulation with a random forest
- add in feature selection methods to LIME input options
- turn repetitive code into functions
- look into iml (https://www.youtube.com/watch?v=jP6Rg13PEkQ)
- look more into Molnar and his adviser Bernd
- Siggi suggests refitting the RF model to the perturbations and then continuing with LIME with the RF predictions from the new model - this may help to understand if the problems are due to the sampling procedure or LIME itself
- he also suggested looking into SMOTE for dealing the inbalance in the classes with sampling
- look back at 601 notes from Kaiser and Hadley's removing the blindfold and
  think about how this could be applied with random forests
- try retriculate to apply python version of lime
- look at 'removing the blindfold' for ideas
- read through Heike's new function
- think of a way to compute consistency across top two features
- compare the simple models based on different number of bins using an F-test
- look into literature on binning methods
- think about why R^2 would be better for some binning methods
- look into computing a diversity or consistency measure for the sensitivity analysis
- create distribution visualizations bins
- include a penalty for the number of parameters when choosing bins
- determine the best number of bins to use for each variable
- look at the AUC after binning
- write a draft of the examiners paper
- try out different weights
- read through LIME papers again
- compute a likelihood ratio prob TRUE / prob FALSE from the LIME ridge regression
- try out logistic regression idea for bins (write own bin list to put in explain)
- try out subsampling idea
- read new paper on Anchor
- read book Dr. Dixon lent me on sensativity analyses
- try visualizing the features from the test data using dimension reduction and
  coloring them by variables suggested to be important by lime
- look into papers by Giles Hooker and Lucas Mentch

>>>>

# LIME Research <img align="right" height="200" src="./figures/lime.png">

@@

- adding a random noise variable to the model to see if LIME ever chooses it as an important variable
- is it okay if I change the repo name to "lime-research"?
- can I remove some of the sources from the references file that I am not going to use?
- I finished writing and editing the introduction - what do you think?

@@

- draft background section
- read through papers giving an overview of the current explanation methods
- create first draft of JSM poster

@@

- LIME diganostics  
    - turn repetitive code into functions
    - try out different weights
    - change distance matrix in seriation to be 5-# of variables shared between two rows
    - try using distance matrix computed on the feature value with seriation
    - add in feature selection methods to LIME input options
    - think of a way to compute consistency across top two features
    - Siggi suggests refitting the RF model to the perturbations and then continuing with LIME with the RF predictions from the new model - this may help to understand if the problems are due to the sampling procedure or LIME itself
    - he also suggested looking into SMOTE for dealing the inbalance in the classes with sampling
    - compare the simple models based on different number of bins using an F-test
    - look into computing a diversity or consistency measure for the sensitivity analysis
    - include a penalty for the number of parameters when choosing bins
    - look at the AUC after binning
    - compute a likelihood ratio prob TRUE / prob FALSE from the LIME ridge regression
    - try visualizing the features from the test data using dimension reduction and
  coloring them by variables suggested to be important by lime
- explainer models
    - look into iml (https://www.youtube.com/watch?v=jP6Rg13PEkQ)
    - look more into Molnar and his adviser Bernd
- understanding LIME
    - read through LIME papers again
    - finish journal on understanding lime (look at the RF in the local region lime is considering to see if it agrees with the lime explanations)
    - try fitting LASSO logistic model and leave one out approach (for multicollinarity)
    - assess lime results on logistic regression models
    - think about how the argmin is accomplished by the LIME R package
    - try retriculate to apply python version of lime
    - look into literature on binning methods
    - think about why R^2 would be better for some binning methods
    - read new paper on Anchor
- simulation with RF
    - think about how to implement a simulation with a random forest
    - look back at 601 notes from Kaiser for model assessment
    - look at Hadley's 'removing the blindfold' for ideas
    - read book Dr. Dixon lent me on sensativity analyses
- possible improvements to LIME
    - determine the best number of bins to use for each variable
    - try out subsampling idea
- random forests confidence intervals
    - look into papers by Giles Hooker and Lucas Mentch
    - Dr. Nettleton paper
